fsOGTT Pre- and Post-ETI

### 2025-12-23 Christine Chan/EnVision CF/fsOGTT_pre_post_ETI.qmd
a bunch of updates for Christine

```{r data cleaning}
setwd(home_dir)
# Import cleaned data
load("./Data_Clean/fsOGTT_pre_post_ETI.RData")
# Subset to people with more than one pre-ETI fsOGTT
multi_pre_df = df |>
  group_by(study_id) |>
  mutate(
    n_pre = sum(pre_post == "Pre"),
    time_diff_first_last = as.numeric(difftime(
      last(Date),
      first(Date),
      units = "days"
    ))
  ) |>
  filter(n_pre > 1)
var_label(multi_pre_df$n_pre) = "Number of fsOGTT pre-ETI"
var_label(multi_pre_df$time_diff_first_last) = "Days From First to Last fsOGTT"
# Save for Christine and Monique
write.csv(
  multi_pre_df,
  file = "./Data_Clean/fsOGTT_pre_post_ETI.csv",
  row.names = F,
  na = ""
)
```

@@

@@

>>>>

```{r data cleaning}
setwd(home_dir)
# Import cleaned data
load("./Data_Clean/fsOGTT_pre_post_ETI.RData")
# Subset to people with more than one pre-ETI fsOGTT
multi_pre_df = df |>
  arrange(study_id, Date) |>
  group_by(study_id) |>
  mutate(
    n_pre = sum(pre_post == "Pre"),
    time_diff_first_last = as.numeric(difftime(
      last(Date),
      first(Date),
      units = "days"
    )),
    time_diff_last_first = as.numeric(difftime(
      first(Date[pre_post == "Post"]),
      last(Date[pre_post == "Pre"]),
      units = "days"
    ))
  ) |>
  filter(n_pre > 1)
var_label(multi_pre_df$n_pre) = "Number of fsOGTT pre-ETI"
var_label(multi_pre_df$time_diff_first_last) = "Days From First to Last fsOGTT"
var_label(
  multi_pre_df$time_diff_last_first
) = "Days From Last Pre-ETI fsOGTT to First Post-ETI fsOGTT"
# Calculate days between pre- and post-ETI fsOGTTs
times = multi_pre_df |>
  group_by(study_id, pre_post) |>
  reframe(d = difftime(Date, lag(Date), units = "days"))
# Save for Christine and Monique
write.csv(
  multi_pre_df,
  file = "./Data_Clean/fsOGTT_pre_post_ETI.csv",
  row.names = F,
  na = ""
)
```

@@

The median number of days between pre-ETI fsOGTTs was `r as.numeric(summary(times$d[times$pre_post=="Pre"])[3])` (IQR: `r as.numeric(summary(times$d[times$pre_post=="Pre"])[2])`, `r as.numeric(summary(times$d[times$pre_post=="Pre"])[5])`). The median number of days between post-ETI fsOGTTs was `r as.numeric(summary(times$d[times$pre_post=="Post"])[3])` (IQR: `r as.numeric(summary(times$d[times$pre_post=="Post"])[2])`, `r as.numeric(summary(times$d[times$pre_post=="Post"])[5])`).

@@

## Matsuda

```{r}
#| warning: false
# Plot
p = ggplot(
  multi_pre_df,
  aes(
    x = years_from_eti_start,
    y = matsuda,
    group = study_id,
    color = study_id
  )
) +
  geom_point() +
  geom_line() +
  theme_bw()
ggplotly(p)
# Model
m = lmer(
  matsuda ~ years_from_eti_start_model + slope_change + (1 | study_id),
  data = multi_pre_df
)
m |>
  tbl_regression(
    exponentiate = F,
    estimate_fun = label_style_sigfig(digits = 4),
    pvalue_fun = label_style_pvalue(digits = 2),
  )
```
